\RequirePackage{xcolor}
\documentclass[fleqn]{fcup-thesis}

\usepackage[english]{babel}
\usepackage{lipsum}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,bm}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage[separate-uncertainty=true]{siunitx}
\usepackage[version=3]{mhchem}
\usepackage{wasysym}
\usepackage[final]{microtype}
\usepackage[hang,multiple]{footmisc}
\let\newfloat\relax
\usepackage{float}
\usepackage{placeins}
\usepackage{xkvltxp}
\usepackage{fixme}
\usepackage{color}
\usepackage{rotate}
\usepackage{rotating}
\usepackage{threeparttable}
\usepackage{threeparttablex}            % Lets threeparttable work with longtable
\usepackage{longtable}
\usepackage{pdflscape}

\usepackage{caption}
\captionsetup{
  labelfont=bf,
}
\captionsetup[table]{%
  justification=justified,
  singlelinecheck=false,
}


\definecolor{flatblue}{RGB}{41, 128, 185}
\definecolor{flatgrey}{RGB}{52, 73, 94}
\definecolor{flatgreen}{RGB}{44, 201, 144}
\definecolor{flatpurple}{RGB}{142, 68, 173}
\definecolor{flatorange}{RGB}{211, 84, 0}
\definecolor{flatred}{RGB}{207, 0, 15}
\usepackage{soul}  % highlight text with \hl{}, strikethrough with \st{}
\sethlcolor{flatgreen}
\setstcolor{flatred}
\usepackage{epigraph} %for quotes
\setlength\epigraphrule{0pt}

%% TODO NOTES
\usepackage{xargs}                      % Use more than one optional parameter in a new commands
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\newcommandx{\change}[2][1=]{\todo[linecolor=flatblue,backgroundcolor=flatblue!25,bordercolor=flatblue,#1]{#2}}
\newcommandx{\reference}[2][1=]{\todo[linecolor=flatgreen,backgroundcolor=flatgreen!25,bordercolor=flatgreen,#1]{#2}}
\newcommandx{\unfinished}[2][1=]{\todo[linecolor=flatorange,backgroundcolor=flatorange!25,bordercolor=flatorange,#1]{#2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=flatpurple,backgroundcolor=flatpurple!25,bordercolor=flatpurple,#1]{#2}}


%%%%%%%%%%% Literature %%%%%%%%%%%%%%%
% When in doubt visit this page:
% http://adsabs.harvard.edu/abs_doc/aas_macros.html
\usepackage[authoryear]{natbib}
\def\aap{A\&A}
\def\aapr{Astronomy and Astrophysics Reviews}
\def\eprint{e-prints}
\def\apj{ApJ}
\def\apjs{ApJS}
\def\apjl{ApJL}
\def\mnras{MNRAS}
\def\aj{AJ}
\def\nat{Nature}
\def\aaps{A\&A Supp.}
\def\pasp{Publications of the ASP}
\def\prd{Phys. Rev. D}
\def\prl{Phys. Rev. Lett.}
\def\araa{ARA\&A}
\def\actaa{Acta Astronomica}
\def\procspie{Proceedings of the SPIE}
\def\pasj{PASJ}
\def\icarus{Icarus}
\def\pasa{Publications of the Astron. Soc. of Australia}


\usepackage{fix-cm} % Allows increasing the f
\usepackage[colorlinks,
           linkcolor=flatorange,
           citecolor=flatblue,
           urlcolor=flatpurple]{hyperref}

\usepackage[Lenny]{fncychap}

%%%%%%%%%%%%% new commands %%%%%%%%%%%%%%%
\newcommand{\cref}[1]{Chapter~\ref{#1}}
\newcommand{\sref}[1]{Section~\ref{#1}}
\newcommand{\tref}[1]{\tablename~\ref{#1}}
\newcommand{\fref}[1]{\figurename~\ref{#1}}
\newcommand{\aref}[1]{Appendix~\ref{#1}}
\newcommand{\eref}[1]{Equation~\ref{#1}}
\renewcommand{\epsilon}{\varepsilon}
\renewcommand{\bf}{\textbf}
\newcommand{\nicebreak}{\newline\newline\noindent}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\object}[1]{#1}
\newcommand{\Mjup}{M_\mathrm{Jup}}

%%%%%%%%%%%%%%%% Math %%%%%%%%%%%%%%%%%%%%
\newcommand{\F}{\mathcal{F}}
\newcommand{\tm}[1]{\textnormal{#1}}
\newcommand{\pd}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\dd}[2]{\frac{\mathrm{d} #1}{\mathrm{d} #2}}

%%%%%%%%%%%%% Layout %%%%%%%%%%%%%%%%%%%%%
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

%% A&A stuff
\DeclareRobustCommand{\ion}[2]{\textup{#1\,\textsc{\lowercase{#2}}}}
\newcommand*\element[1][]{%
  \def\aa@element@tr{#1}%
  \aa@element
}


%% *** Change this example to appropriate values. ***
\degree{Doctor of Philosophy}
\department{Departamento de Fisica e Astronomia}
\gradyear{2017}
\author{Daniel Thaagaard Andreasen}
\title{Determination of stellar parameters for M-dwarf stars: the NIR approach}


%% Make each page fill up the entire page.
\flushbottom


%%%%%%%%%%%%      MAIN  DOCUMENT      %%%%%%%%%%%%
% \includeonly{introduction}

\begin{document}

%% This sets the page style and numbering for preliminary sections.
\begin{preliminary}

%% This generates the title page from the information given above.
\maketitle
\cleardoublepage


\begin{dedication}
\centering \huge \itshape
To Linnea, Henriette, Rico, and Else\\For always supporting me
\end{dedication}


\begin{acknowledgements}

When doing a PhD it is important to remember it is more a team effort than the work of an
individual. This is something I learned quickly during the last four years. Therefore there are
several people I would like to thank.

First and most importantly are my two supervisors, S\'{e}rgio and Nuno. They were after me in the
beginning of my studies because I was too shy to ask for help; something that I quickly learned I
needed to do. They always had their door open for me and all my small questions. It goes without
saying that I am thankful for all their guidance during my studies. However, what I am most thankful
for is the freedom I have had to explorer paths and ideas on my own, and with them safely on the
sideline. This sometimes led to failures and dead ends, but it make me grow as a researcher both by
learning from my mistake, but also by prioritising my time.

When I thank S\'{e}rgio and Nuno, my official supervisors, I also have to thank Elisa. She has been
my third unofficial supervisor almost from the first day. Although she did not have any experience
with NIR spectroscopy, she was never afraid of giving her opinion and trying to help. Elisa, your
kindness, calmness, and help is priceless! It is extremely reassuring to go on this adventure with
three capable supervisors ready to help at any time.

While S\'{e}rgio, Nuno, and Elisa are all very capable, they were not alone to answer all my
technical questions. Often I went to Vardan to discuss science. Vardan's knowledge is immense, and
it has been a pleasure to receive advise and answers when necessary. Similar has the support from
Maria in my first two years been valuable. She was my friend here when I arrived, and the one I went
to in the beginning with small questions since I was too shy to go with ``stupid'' questions to my
supervisors. Thanks for all the answers you both gave me and the fruitful collaborations.

Luckily my time here in Porto has not only been about work. I have had a lot of good times with new
and old friends here. In a random order I would like to thank Elisa, Maria, Jo\~{a}o, Jorge,
B\’{a}rbara, Jason, Vardan, Mahmoud, Guilherme, Giancarlo, Andressa, Luisa, Solène, and the entire
football team.

A very special thank you to Sofia who made my life easier here in Portugal, and has been a fantastic
support and friend. All your time and effort will never be forgotten, and I appreciate all you have
done for me.

Now, I know being abroad has been difficult but exciting for me. However, it has mostly been
difficult for my family home in Denmark. The last part is specifically dedicated to them: Tusind tak
for al jeres tålmodighed, mine kære venner og familie i Danmark. Jeg ved jeg ikke altid har været
den bedste til at sende et par beskeder hjem, men alligevel har I altid mødt mig med kram når I har
hentet mig i lufthavnen. Det har været en svær tid for mig her, og at tænke på jer derhjemme har
virkelig holdt mit mod oppe! Jeg vil i sær gerne takke mine søstre, Henriette og Linnea for altid at
have tid til at sludre lidt. Det samme gælder Rico, som også har hentet mig et par gange i
lufthavnen. Selvfølgelig bliver jeg nødt til at sige tak til min kære mormor. Din støtte har været
uden lige. Der har også altid været mange venner derhjemme som har fundet tid til at bruge et par
timer med mig. Tusind tak til i sær Ole, Jesper, Ellen Marie, Maria, Ditte, og Sabrina.

\vspace{7mm}
Tusind tak alle sammen/thank you very much everybody!


\end{acknowledgements}



\begin{abstract}

In this thesis, I describe the process of deriving stellar atmospheric parameters for FGK stars
using high resolution and high signal-to-noise ratio near-IR spectra. The effort presented here is
the first step towards analysing the cooler and more atmospheric complex M stars. Our own galaxy,
The Milky Way, consist of around 75\% M stars, thus studying these stars is a study of the galaxy:
galactic archaeology. Additionally, these stars are prone to form low-mass rocky planets, making
them ideal targets for habitable Earth-like planets.

In Chapter 2 and 3 I will introduce the theory needed for spectroscopic analysis and the methodology
for the actual study. Especially in Chapter 3 I will present an automatic tool for deriving stellar
atmospheric parameters, \code{FASMA}. This tool can derive parameters for solar-type stars in both
the optical and the NIR and is used throughout the thesis.

After setting up the theory and methodology I will in Chapter 4 present the results from my studies
in the NIR. These will start with a compilation of a NIR iron line list used for the spectroscopic
analysis. This is then used to successfully study four stars with varying spectral type; the Sun, one
hotter than the Sun, and two cooler. Due to lack of NIR spectra, I choose to analyse some synthetic
spectra as well which is also presented in Chapter 4.

Part of the thesis was dedicated to the continuous update of SWEET-Cat, a database of planet host
stars. This lead to a paper presenting 50 planet host parameters derived in a homogeneous and
consistent way. The analysis of 50 planet hosts is followed by another work discovering two giant
planet populations; a study I was part of.

With this thesis, another few pieces has been put in the NIR spectroscopy puzzle, preparing for the
next pieces as well, which will be the study of M stars. This will then lead to the studies of the
tinniest rocky planets to the galaxy.


\end{abstract}

\begin{abstract-pt}


Nesta tese, descrevo o processo de deriva\c{c}\~{a}o de par\^{a}metros de atmosferas de estrelas FGK
usando espectros de infra-vermelho de alta resolu\c{c}\~{a}o e de elevado sinal-sobre-ru\’{\i}do. O
esfor\c{c}o aqui apresentado representa o primeiro passo para derivar par\^{a}metros
atmosf\'{e}ricos de estrelas mais frias (estrelas M) onde a an\’{a}lise espectrosc\’{o}pica \'{e}
bem mais complexa. Notar que na nossa pr\’{o}pria gal\’{a}xia, a Via L\’{a}ctea, cerca de 75\% de
todas as estrelas s\~{a}o de estrelas M, pelo que estudar estas estrelas \'{e} tamb\'{e}m um passo
importante para o estudo da nossa gal\’{a}xia, tamb\'{e}m denominada por arqueologia gal\’{a}ctica.
Estas estrelas s\~{a}o tamb\'{e}m as mais propensas a formar planetas rochosos de baixa massa,
tornando-as alvos ideais para a detec\c{c}\~{a}o de planetas habit\’{a}veis parecidos com a Terra.

Nos Cap\’{\i}tulos 2 e 3 vou apresentar a teoria necess\’{a}ria para a an\’{a}lise
espectrosc\’{o}pica e a metodologia usada no trabalho aqui apresentado. Em especial no Cap\’{\i}tulo
3 irei apresentar uma ferramenta autom\’{a}tica para a deriva\c{c}\~{a}o de par\^{a}metros
estelares, FASMA. Esta ferramenta pode derivar par\^{a}metros para estrelas de tipo solar quer
usando espectros no vis\’{\i}vel quer no infra-vermelho pr\’{o}ximo. Esta ferramenta \'{e} usada em
toda a tese. Depois de apresentar a teoria e a metodologia, no Cap\’{\i}tulo 4 apresento os
resultados dos meus trabalhos desenvolvidos no infra-vermelho-pr\’{o}ximo, come\c{c}ando com uma
compila\c{c}\~{a}o de uma lista de riscas espectrais de Ferro usada para a an\’{a}lise
espectrosc\’{o}pica. Esta lista \'{e} posteriormente usada para estudar com sucesso quatro estrelas
de diferentes classes espectrais: o Sol, uma estrela mais quente do que o Sol e duas estrelas mais
frios do que o Sol. Devido \'{a} escassez de espectros de infra-vermelho, optou-se tamb\'{e}m por
analisar alguns espectros sint\'{e}ticos.

Parte da tese foi dedicada \'{a} atualiza\c{c}\~{a}o constante do SWEET-Cat, uma base de dados para
estrelas com planetas detetados. Deste trabalho escrevi um artigo onde s\~{a}o apresentados novos
par\^{a}metros estelares para 50 estrelas com planetas que foram derivados de uma forma
homog\'{e}nea e consistente. Posteriormente \'{a} an\’{a}lise destas 50 estrelas contribui
tamb\'{e}m para um trabalho onde se descobriu a poss\’{\i}vel presen\c{c}a de duas
popula\c{c}\~{o}es de planetas gigantes.

Esta tese permitiu n\~{a}o s\’{o} adicionar novas pe\c{c}as no complicado puzzle da espectroscopia
no infra-vermelho NIR, mas tamb\'{e}m abriu caminho para o desenvolvimento de novas pe\c{c}as para
completar o puzzle que ser\’{a} o estudo das estrelas M que ser\’{a} importante para o estudo dos
planetas rochosos mais conhecemos na nossa gal\’{a}xia.

\end{abstract-pt}



\tableofcontents
\addcontentsline{toc}{chapter}{\listtablename}
\listoftables
\addcontentsline{toc}{chapter}{\listfigurename}
\listoffigures

\end{preliminary}


%% *** Include chapter files here. ***
\include{introduction}
\include{theory}
\include{method}
\include{results}
\include{sweetcat}
\include{future}


\appendix

\include{nirLineList}
\include{SCtables}
\include{fasmaML}


%% This adds a line for the Bibliography in the Table of Contents.
\addcontentsline{toc}{chapter}{Bibliography}
% \bibliographystyle{plain}
%% *** Set the bibliography file. ***
\bibliography{thesis}
\bibliographystyle{astron}
\nocite{} %include everything.


\end{document}
